Supplementary Tables

### 2019-12-27 Supplementary_tables.Rmd
NAR_submission files 27 Dec 2019

---
title: "Supplementary Tables"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "16 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{caption}
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

```{r, eval=FALSE, include=FALSE}
library(xtable)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
library(gt)

@@

@@

+ [@helwak_mapping_2013; @moore_mirnatarget_2015] reported the energy values in miRNA:target interactions.
+ Comparisons of canonical seed types were evaluated by study of [@grimson_microrna_2007], while functional and non-functional seed interactions were studied by [@bartel_micrornas:_2009] and [@betel2010comprehensive]. 
+ Numeric definition of target region location effect was performed based on studies of [@hausser_analysis_2013] and [@helwak_mapping_2013]

\begin{table}[ht]
\centering
\caption{ Efficiency factors for binding regions on targets}
\begin{tabular}{rlr}
  \hline
 & region & region\_effect \\ 
  \hline
1 & 3UTR & 0.84 \\ 
  2 & CDS & 0.42 \\ 
  3 & 3UTRCDS & 0.93 \\ 
  4 & 5UTR & 0.01 \\ 
  5 & 5UTRCDS & 0.42 \\ 
  6 &  & 0.01 \\ 
  7 & intron & 0.01 \\ 
  8 & CDS3UTR & 0.93 \\ 
  9 & CDS5UTR & 0.42 \\ 
  10 & exon\_unclassified & 0.20 \\ 
  11 & CDS3UTRintron & 0.93 \\ 
  12 & 3UTRintron & 0.84 \\ 
  13 & CDSintron & 0.42 \\ 
  14 & 5UTRintron & 0.01 \\ 
  15 & 5UTR3UTR & 0.93 \\ 
  16 & CDS5UTR3UTR & 0.93 \\ 
   \hline
\end{tabular}
\end{table}

|Hugo_Symbol| miRNA_name | mirna_RPM | GE_normal | energy | seed_type_effect | region_effect |
|-----------|------------|----------|----------------|---------|-----------|----------|
| ENAH | hsa-let-7a-5p | 111204.15 | 7540 | -22.70 | 0.01 | 0.00 |
| GALNT2 | hsa-let-7a-5p | 111204.15 | 2824 | -20.50 | 0.14 | 0.00 | 
| RLF | hsa-let-7a-5p | 111204.15 | 1144 | -18.00 | 0.03 | 0.20 |
| MAST2 | hsa-let-7a-5p | 111204.15 | 2640 | -22.60 | 0.24 | 0.00 | 
| DOCK1 | hsa-let-7a-5p | 111204.15 | 4826 | -20.50 | 0.01 | 0.00 | 
| ZBTB16 | hsa-let-7a-5p | 111204.15 | 315 | -24.30 | 0.14 | 0.00 |

Table: Example of E9GE_mirnagenenormal dataset.

 \begin{table}[ht]
\centering
\caption{ miRNA:target pairs supported by High-throughput Experiments}
\begin{tabular}{lll}
  \hline
 Variable & Structure & Means \\
  \hline
   cluster    & character & Barcode from experimentally method \\
   chromosome    & character & Chromosome of Target gene from raw data \\
   start\_position    & numeric & Gene start position from raw data \\
   end\_position     & numeric & Gene end position from raw data \\
   strand     & character & Gene strand \\
   hgnc\_symbol     & character & Gene name (Symbol) \\
   Ensembl\_Gene\_Id     & character & Ensembl Gene Id of gene \\
   Ensembl\_Transcript\_Id   & character & Ensembl transcript id of mRNA of Target gene \\
   target\_seq   & character & mRNA sequences targeted by miRNA \\
   miRNA   & character & miRNA id (from miRBase version 21 ) \\
   miR\_seq   & character & miRNA sequence \\
   seed\_type   & character & seed type of miRNA:target interaction \\
   Energy   & numeric & Energy of miRNA:target binding \\
   HG38build\_loc   & character & Recent chromosomal location of Gene \\
   Genome\_build   & character& Genome build of given chromosome, start and end positions \\
   region   & character & interaction location on target \\ 
   region\_effect   & numeric & Coefficient of location on target \\ 
   seed\_type\_effect   & numeric & Coefficient for seed sequence of miRNA:target interaction \\
   \hline
\end{tabular}
\end{table}

@@

 \begin{table}[ht]
\centering
\caption{ The context graph object during the process.}
\begin{tabularx}{\textwidth}{llX}
  \hline
 Variables & Structure & Means \\
  \hline
   \emph{Node Variables} & & \\
   name    & character & node name \\
   type    & character &Competing or miRNA \\
   node\_id    & numeric & in on graph object \\
   initial\_count     & numeric & Initial Expression value of node \\
   count\_pre     & numeric & Expression value of node at previous regulation \\
   count\_current     & numeric & Existing expression value of node \\
   changes\_variable     & character & Regulation of node (Up, down or steady) \\
   \hline
   \emph{Edge Variables} & & \\
   Competing name   & character & name of genes\\
   miRNA name   & character & name of miRNAs \\
   Competing expression   & numeric & Expression values of competing elements at steady-state \\
   miRNA expression   & numeric & Expression values of miRNA elements at steady-state \\
   energy   & numeric & coefficient of miRNA:target interactions (binding affinity) \\
   seed type   & numeric & coefficient of miRNA:target interactions (binding affinity) \\
   region   & numeric & coefficient of miRNA:target interactions (degradation efficiency) \\
   afff factor   & numeric& coefficient scaled and combined affinity factor \\
   degg factor   & numeric &coefficient scaled and combined degradation factor \\ 
   comp\_count\_list   & list & list of competing expression for each iteration \\ 
   comp\_count   & numeric & pre: competing expression at previous iteration; current: competing expression at present iteration \\
   mirna\_count\_list   & list & list of miRNA expression for each iteration \\
   mirna\_count   & numeric & pre: miRNA expression at previous iteration; current: miRNA expression at present iteration \\
   effect   & numeric & pre: total miRNA reppressive effect on individual target at previous iteration ; current: miRNA reppressive effect on individual   target at present iteration \\
   effect\_list   & list & list of miRNA reppressive effect on individual target for each iteration \\
  \hline
\end{tabularx}
\end{table}

@@

## REFERENCES

>>>>

---
title: "Supplementary Tables"
author: 
- Selcen Ari Yuka
- Alper Yilmaz 
date: "`r Sys.Date()`"
output: pdf_document 
bibliography: NAR-sample.bib
header-includes: 
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{caption}
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

```{r, eval=FALSE, include=FALSE}
library(xtable)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=30),tidy=TRUE)
library(gt)

@@

\begin{table}[ht]
\centering
\caption{ Efficiency factors for binding regions on targets}
\begin{tabular}{rlr}
  \hline
 & region & region\_effect \\ 
  \hline
1 & 3UTR & 0.84 \\ 
  2 & CDS & 0.42 \\ 
  3 & 3UTRCDS & 0.93 \\ 
  4 & 5UTR & 0.01 \\ 
  5 & 5UTRCDS & 0.42 \\ 
  6 & none & 0.01 \\ 
  7 & intron & 0.01 \\ 
  8 & CDS3UTR & 0.93 \\ 
  9 & CDS5UTR & 0.42 \\ 
  10 & exon\_unclassified & 0.20 \\ 
  11 & CDS3UTRintron & 0.93 \\ 
  12 & 3UTRintron & 0.84 \\ 
  13 & CDSintron & 0.42 \\ 
  14 & 5UTRintron & 0.01 \\ 
  15 & 5UTR3UTR & 0.93 \\ 
  16 & CDS5UTR3UTR & 0.93 \\ 
   \hline
\end{tabular}
\end{table}

@@

+ Helwak et al. [-@helwak_mapping_2013] and Moore et al.[- @moore_mirnatarget_2015] reported the energy values in miRNA:target interactions.
+ Comparisons of canonical seed types were evaluated by study of Grimson et al. [-@grimson_microrna_2007], while functional and non-functional seed interactions were studied by Bartel et al. [-@bartel_micrornas:_2009] and Betel et al. [-@betel2010comprehensive] (Table S2). 
+ Numeric definition of target region location effect was performed based on studies of Hausser et al. [-@hausser_analysis_2013] and Helwak et al. [-@helwak_mapping_2013] (Table S3).

|Hugo Symbol| miRNA name | mirna RPM | GE normal | energy | seed type effect | region effect |
|-----------|------------|----------|----------------|---------|-----------|----------|
| ENAH | hsa-let-7a-5p | 111204.15 | 7540 | -22.70 | 0.01 | 0.00 |
| GALNT2 | hsa-let-7a-5p | 111204.15 | 2824 | -20.50 | 0.14 | 0.00 | 
| RLF | hsa-let-7a-5p | 111204.15 | 1144 | -18.00 | 0.03 | 0.20 |
| MAST2 | hsa-let-7a-5p | 111204.15 | 2640 | -22.60 | 0.24 | 0.00 | 
| DOCK1 | hsa-let-7a-5p | 111204.15 | 4826 | -20.50 | 0.01 | 0.00 | 
| ZBTB16 | hsa-let-7a-5p | 111204.15 | 315 | -24.30 | 0.14 | 0.00 |

Table: Example of E9GE_mirnagenenormal dataset. Hugo Symbol, gene symbol; miRNA name, name of miRNA that interacted with specified gene; mirna RPM; mirna count in read per million; seed type and region effect, numeric seed type and region coefficients for specified miRNA:gene interactions based on Table S2 and S3.

\newpage
 \begin{table}[ht]
\centering
\caption{ Context of miRNA:target pairs dataset supported by High-throughput Experiments}
\begin{tabular}{lll}
  \hline
 Variable & Structure & Means \\
  \hline
   cluster    & character & Barcode from experimentally method \\
   chromosome    & character & Chromosome of Target gene from raw data \\
   start\_position    & numeric & Gene start position from raw data \\
   end\_position     & numeric & Gene end position from raw data \\
   strand     & character & Gene strand \\
   hgnc\_symbol     & character & Gene name (Symbol) \\
   Ensembl\_Gene\_Id     & character & Ensembl Gene Id of gene \\
   Ensembl\_Transcript\_Id   & character & Ensembl transcript id of mRNA of Target gene \\
   target\_seq   & character & mRNA sequences targeted by miRNA \\
   miRNA   & character & miRNA id (from miRBase version 21 ) \\
   miR\_seq   & character & miRNA sequence \\
   seed\_type   & character & seed type of miRNA:target interaction \\
   Energy   & numeric & Energy of miRNA:target binding \\
   HG38build\_loc   & character & Recent chromosomal location of Gene \\
   Genome\_build   & character& Genome build of given chromosome, start and end positions \\
   region   & character & interaction location on target \\ 
   region\_effect   & numeric & Coefficient of location on target \\ 
   seed\_type\_effect   & numeric & Coefficient for seed sequence of miRNA:target interaction \\
   \hline
\end{tabular}
\end{table}

@@

 \begin{table}[ht]
\centering
\caption{ The context of graph object during the process.}
\begin{tabularx}{\textwidth}{llX}
  \hline
 Variables & Structure & Means \\
  \hline
   \emph{Node Variables} & & \\
   name    & character & node name \\
   type    & character &Competing or miRNA \\
   node\_id    & numeric & in on graph object \\
   initial\_count     & numeric & Initial Expression value of node \\
   count\_pre     & numeric & Expression value of node at previous regulation \\
   count\_current     & numeric & Existing expression value of node \\
   changes\_variable     & character & Regulation of node (Up, down or steady) \\
   \hline
   \emph{Edge Variables} & & \\
   Competing name   & character & name of genes\\
   miRNA name   & character & name of miRNAs \\
   Competing expression   & numeric & Expression values of competing elements at steady-state \\
   miRNA expression   & numeric & Expression values of miRNA elements at steady-state \\
   energy   & numeric & coefficient of miRNA:target interactions (binding affinity) \\
   seed type   & numeric & coefficient of miRNA:target interactions (binding affinity) \\
   region   & numeric & coefficient of miRNA:target interactions (degradation efficiency) \\
   afff factor   & numeric& coefficient scaled and combined affinity factor \\
   degg factor   & numeric &coefficient scaled and combined degradation factor \\ 
   comp\_count\_list   & list & list of competing expression for each iteration \\ 
   comp\_count   & numeric & pre: competing expression at previous iteration; current: competing expression at present iteration \\
   mirna\_count\_list   & list & list of miRNA expression for each iteration \\
   mirna\_count   & numeric & pre: miRNA expression at previous iteration; current: miRNA expression at present iteration \\
   effect   & numeric & pre: total miRNA reppressive effect on individual target at previous iteration ; current: miRNA reppressive effect on individual   target at present iteration \\
   effect\_list   & list & list of miRNA reppressive effect on individual target for each iteration \\
  \hline
\end{tabularx}
\end{table}

@@

# REFERENCES
